---
title: "Homework_08"
author: "David Green"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

When the LATD/NIP gene in *Medicago truncatula* is made inactive the root lengths of the plants are shorter.

The expected primary root lengths of the wild type (A17) plants are 17 cm with a standard deviation of 2. The expected primary root lengths of the mutant (*latd*) plants are 6 cm with a standard deviation of 2.

### Simulation 1

#### Mean: Control = 17, latd = 6

```{r}
control <- rnorm(n = 28, mean = 17, sd = 2) 
latd <- rnorm(n = 28, mean = 6, sd = 2)
df <- data.frame(control, latd)
t_test <- t.test(latd, control)
print(t_test)
boxplot(control, latd, 
        names = c('Control', 'latd'),
        ylab = 'Primary Root Length',
        title = 'Primary root Length: latd vs. Wild')
```

#### Mean: Control = 17, latd = 10

```{r}
control <- rnorm(n = 28, mean = 17, sd = 2) 
latd <- rnorm(n = 28, mean = 10, sd = 2)
df <- data.frame(control, latd)
t_test <- t.test(latd, control)
print(t_test)
boxplot(control, latd, 
        names = c('Control', 'latd'),
        ylab = 'Primary Root Length',
        title = 'Primary root Length: latd vs. Wild')
```

#### Mean: Control = 17, latd = 15

```{r}
control <- rnorm(n = 28, mean = 17, sd = 2) 
latd <- rnorm(n = 28, mean = 15, sd = 2)
df <- data.frame(control, latd)
t_test <- t.test(latd, control)
print(t_test)
boxplot(control, latd, 
        names = c('Control', 'latd'),
        ylab = 'Primary Root Length',
        title = 'Primary root Length: latd vs. Wild')
```

The lowest that I am able to go with the mean of the *latd* group is 15 before I get above a p-value of 0.05.

#### Sample size: 15

```{r}
control <- rnorm(n = 15, mean = 17, sd = 2) 
latd <- rnorm(n = 15, mean = 6, sd = 2)
df <- data.frame(control, latd)
t_test <- t.test(latd, control)
print(t_test)
boxplot(control, latd, 
        names = c('Control', 'latd'),
        ylab = 'Primary Root Length',
        title = 'Primary root Length: latd vs. Wild')
```

#### Sample size: 5

```{r}
control <- rnorm(n = 5, mean = 17, sd = 2) 
latd <- rnorm(n = 5, mean = 6, sd = 2)
df <- data.frame(control, latd)
t_test <- t.test(latd, control)
print(t_test)
boxplot(control, latd, 
        names = c('Control', 'latd'),
        ylab = 'Primary Root Length',
        title = 'Primary root Length: latd vs. Wild')
```

#### Sample size: 2

```{r}
control <- rnorm(n = 2, mean = 17, sd = 2) 
latd <- rnorm(n = 2, mean = 6, sd = 2)
df <- data.frame(control, latd)
t_test <- t.test(latd, control)
print(t_test)
boxplot(control, latd, 
        names = c('Control', 'latd'),
        ylab = 'Primary Root Length',
        title = 'Primary root Length: latd vs. Wild')
```

If I make the sample size 2 I still get a p-value that is below 0.05. 2 Is the lowest that I can go without getting an error in the t.test.


