---
title: "Homework_12"
author: "David C. Green"
date: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(patchwork)
```

---

Here are two graphs that are for nodualtion experiments that I have ran in the past.

The first graph is for the experimental data looking at the effect of inoculation, during salt stress, on lateral root density

```{r}
filePath1 <- 'Random_NOD_Data/rand_nod1.csv'
table1 <- read.table(filePath1, header = TRUE, sep = ',')
filePath2 <- 'NodData/MSSR108_POOL_NODEAD_RAW.csv'
table2 <- read.table(filePath2, header = TRUE, sep = ',')
# boxplot for experimental nod data
plot2 <- ggplot(table2, aes(x = Treatment, y = LR, fill = Inoculation)) +
  geom_boxplot() +
  xlab('Treatment') +
  ylab('PRL') +
  ggtitle('Lateral Root Density During Moderate Salt Stress')

print(plot2)
```

---

The second graph is for the simulated randomized data 

```{r}
# boxplot for random nod data
plot1 <- ggplot(table1, aes(x = Treatment, y = LR, fill = Inoculation)) +
  geom_boxplot() +
  xlab('Treatment') +
  ylab('PRL') +
  ggtitle('Lateral Root Density During Moderate Salt Stress Using Simulated Data')

print(plot1)
```

---

Now here is a graph for some mythical data that I created. I wanted to mess around with making a heat map.

```{r}
Sheeva <- sample(c(rep('Mardiel', 100), rep('Gramital', 100), rep('Hormal', 100), rep('Sidel', 100)))
Sental <- sample(c(rep('Horn', 50), rep('Sheeve', 50), rep('Stral', 50), rep('Grift', 50), rep('Freal', 50), rep('Trill', 50), rep('Sogor', 50), rep('Raydal', 50)))
Corisent <- runif(400)
df1 <- data.frame(Sheeva, Sental, Corisent)

# heatmap for fantasy data
plot3 <- ggplot(df1, aes(x = Sheeva, y = Sental, fill = Corisent)) +
  geom_tile() +
  ggtitle('Chiveral of Gorintal') +
  xlab('Sheeva') +
  ylab('Sental')
print(plot3)
```

---

I decided to mess around with facetting too

```{r}
plot4 <- ggplot(table2, aes(x = Treatment, y = LR)) +
  geom_boxplot()
print(plot4)
plot4 + facet_grid(.~Inoculation)
```

